Water Management

### 2020-02-12 Paper/paper.tex
more results on rainfall distributions

	\begin{figure}[ht]
		\includegraphics[width=1\textwidth]{figures/steadyStateMonteCarlo.eps}
		\caption{Steady State Probability}
		\label{fig:steadyStateMonteCarlo}
	\end{figure}
	\subsection{Effect of Changed Discount Factors to Optimal Irrigation Policy}
	When altering the discount factor $\beta$ in a range from 0 to 1, the optimal irrigation policy changes.
	Looking at small water levels within the reservoir the optimal irrigation amount does not change much depending on the discount factor.
	A small $\beta$ ensures that high water levels at the end of one period are only available to a small extent in the next period. 
	This leads to a increasing gap between irrigation amounts over $\beta$ with increasing water level since conserving water does not increase the usage as much.
	One can say that a high $\beta$ prefers a long-term policy while a smaller $\beta$ leads to a rather short-term policy.
	\begin{figure}[ht]
		\includegraphics[width=1\textwidth]{figures/optimum-policy-over-beta.eps}
		\caption{Optimal irrigation policy as a function of the discount factor $\beta$}
		\label{fig:optimal-irrigation-beta}
	\end{figure}
	\newpage
	\subsection{Changed Volatility of Rainfalls}
	A more volatile rainfall means a rainfall having a higher standard deviation.
	Since we want to compare two rainfall distributions of the same mean, the median of the distribution has to be changed.
	Using a $\sigma^2=2$ includes a mean of $\mu=-1.5$ in order for the mean to stay the same. 
	(See \ref{eq:rainfall} for reference) 
	\begin{equation}
		mean = exp(\mu+\frac{\sigma^2}{2}) \label{eq:rainfall}
	\end{equation} 
	Both distributions are visualized in \ref{fig:rain-distributions}.
	\begin{figure}
		\begin{subfigure}{0.5\textwidth}
			\centering
			\includegraphics[width=1\textwidth]{figures/rainfall-default.eps}
			\caption{$\mu=0, \sigma=1$}
			\label{fig:rainfall-default}
		\end{subfigure}%
		\begin{subfigure}{.5\textwidth}
			\centering
			\includegraphics[width=1\textwidth]{figures/rainfall-more-volatile.eps}
			\caption{$\mu=-1.5, \sigma=2$}
			\label{fig:rainfall-changed}
		\end{subfigure}
		\caption{Different Rain Distributions}
		\label{fig:rain-distributions}
	\end{figure}
	\newpage
	\printbibliography

>>>>

		\includegraphics[width=1\textwidth]{figures/steadyStateMonteCarlo.eps}
		\caption{Steady State Probability}
		\label{fig:steadyStateMonteCarlo}
	\subsection{Effect of Changed Discount Factors to Optimal Irrigation Policy}
	When altering the discount factor $\beta$ in a range from 0 to 1, the optimal irrigation policy changes.
	Looking at small water levels within the reservoir the optimal irrigation amount does not change much depending on the discount factor.
	A small $\beta$ ensures that high water levels at the end of one period are only available to a small extent in the next period. 
	This leads to a increasing gap between irrigation amounts over $\beta$ with increasing water level since conserving water does not increase the usage as much.
	One can say that a high $\beta$ prefers a long-term policy while a smaller $\beta$ leads to a rather short-term policy.
		\includegraphics[width=1\textwidth]{figures/optimum-policy-over-beta.eps}
		\caption{Optimal irrigation policy as a function of the discount factor $\beta$}
		\label{fig:optimal-irrigation-beta}
	\subsection{Changed Volatility of Rainfalls}
	A more volatile rainfall means a rainfall having a higher standard deviation.
	Since we want to compare two rainfall distributions of the same mean, the median of the distribution has to be changed.
	Using a $\sigma^2=2$ includes a mean of $\mu=-1.5$ in order for the mean to stay the same. 
	(See \ref{eq:rainfall} for reference) 
	\begin{equation}
		mean = exp(\mu+\frac{\sigma^2}{2}) \label{eq:rainfall}
	\end{equation} 
	Both distributions are visualized in \ref{fig:rain-distributions}.
	\begin{figure}
		\begin{subfigure}{0.5\textwidth}
			\centering
			\includegraphics[width=1\textwidth]{figures/rainfall-default.eps}
			\caption{$\mu=0, \sigma=1$}
			\label{fig:rainfall-default}
		\end{subfigure}%
		\begin{subfigure}{.5\textwidth}
			\centering
			\includegraphics[width=1\textwidth]{figures/rainfall-more-volatile.eps}
			\caption{$\mu=-1.5, \sigma=2$}
			\label{fig:rainfall-changed}
		\end{subfigure}
		\caption{Different Rain Distributions}
		\label{fig:rain-distributions}
		\includegraphics[width=1\textwidth]{figures/aggregated-use-rainfall-default.eps}
		\caption{Aggregated Use for lognormal distributed rainfall $(\mu=0, \sigma=1)$}
		\label{fig:aggregated-use-rainfall-default}
	\includegraphics[width=1\textwidth]{figures/aggregated-use-rainfall-more-volatile.eps}
	\caption{Aggregated Use for lognormal distributed rainfall $(\mu=-1.5, \sigma=2)$}
	\label{fig:aggregated-use-rainfall-more-volatile}
	\ref{fig:aggregated-use-rainfall-default} shows the aggregated use of a lognormal distributed rainfall including the water level, the amount of water used for irrigation in the rain exemplary for 100 periods. \ref{fig:aggregated-use-rainfall-more-volatile} does the same for a changed lognormal distribution parameterized with $\mu=-1.5$ and $\sigma=2$.
	When comparing both visualizations, it is noticeable that more volatile rainfall leads to much higher peaks of rain in combination with reduced number of periods with a decent amount of rain. 
	As a consequence the water level in the reservoir fluctuates much more leading to periods with almost no water in the reservoir. 
	In such periods the farmers use almost no water for irrigation.
	The aggregated use of farmers and recreational users drops significantly.
	Since the reservoir is capped at a amount of 7, the high peaks of rainfall can not be used to a large extent to fill up the reservoir.
	Generally speaking, one can say that a more volatile rain distribution leads to a lower average water level in the reservoir with lower amounts of water to be used for irrigation.
	This effect is reflected in the aggregated use as well. 
	The Use of more volatile rainfall is much lower compared to rainfall parameterized with $\mu=0$ and $\sigma=1$.
	\clearpage	
	\printbibliography
